Binarity's Biases on Transit Survey Occurrence Rates

### 2018-02-23 paper/main.tex
jnw discussion edits

To compute the apparent occurrence rate density, we need to make
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different.  For a given value of $r\a$, the
  number of binary systems in the searchable sample with mass ratio
  $(q, q+\mathrm{d}q)$ is
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
To obtain the total number of searchable binaries,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$. The
result of the integration replaces ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

\section{Discussion}
\label{sec:discussion}

\paragraph{How bad is ignoring binarity?}
This study has shown that under a reasonable set of simplifying
assumptions, ignoring binarity introduces systematic errors to star
and planet counts in transit surveys, which then biases derived
occurrence rates.  Thus far, occurrence rate calculations\footnote{ A
list of occurrence rate papers is maintained at
\url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, it seems that no one
has yet carefully assessed binarity's importance, or lack thereof.
This study does not resolve the problem; it only suggests the
approximate scale of the systematic errors.  Section~\ref{sec:model_2}
suggests that for apparent radii above $2r_\oplus$, binarity can be
ignored down to a precision of a few percent.  For apparent radii
below $2r_\oplus$, the picture is less forgiving:
Section~\ref{sec:model_3} suggests that the apparent rates around
single stars could be overestimated by as much as 50\%.

\paragraph{The rate of Earth analogs}
\citet{youdin_exoplanet_2011},~\citet{petigura_prevalence_2013},~\citet{dong_fast_2013},~\citet{foreman-mackey_exoplanet_2014},
and~\citet{burke_terrestrial_2015} have found that between $0.03$ and
$1$ Earth-like planets exist per Sun-like star, depending on
assumptions that are made when calculating the
rate~\citep[see][Figure~17]{burke_terrestrial_2015}.  Assuming a
broken power-law, we showed that unrecognized binaries could cause
overestimates in the rate of Earth analogs of up to 50\%.  This
systematic effect is smaller than the other factors that currently
dominate the dispersion in $\eta_\oplus$ measurements.  If future
analyses determine absolute values of $\eta_\oplus$ to better than a
factor of two, binarity will likely merit closer attention.

One caveat is that none of our models included the rate density's
period-dependence. However, binaries with separations $\lesssim
10\,{\rm AU}$ could provoke dynamical instabilities, leading to fewer
Earth-like planets per
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
kraus_impact_2016}.  This would affect transit survey measurements of
$\eta_\oplus$ beyond our rough estimate.

\paragraph{Hot Jupiter rate discrepancy}
While unresolved binaries may bias $\eta_\oplus$ measurements, our
approach suggests that they do not influence the hot Jupiter rate
discrepancy.  The ``discrepancy'' is that RV surveys find roughly
twice as many hot Jupiters per Sun-like star as do transit surveys
(roughly $1\%$~vs.~$0.5\%$, respectively).  We summarize hot
Jupiter rates reported by different surveys in
Table~\ref{tab:hj_rates}.

Though the disagreement is only weakly significant ($<3\sigma$), one
reason to expect a difference is that the RV sample is biased towards
metal-rich stars, which host more giant
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005,gould_frequency_2006}.
Investigating the discrepancy from the metallicty
angle,~\citet{guo_metallicity_2017} measured the {\it Kepler} field's
mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= -0.045\pm0.009$,
which is lower than the California Planet Search's mean of $[{\rm
M/H}]_{\rm CPS}= -0.005\pm0.006$.  The former value agrees with that
found by \citet{dong_metallicities_2014}.  Refitting for the
metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta [{\rm
M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm
0.7$, and noted that the metallicity difference could account for
0.2\% of the needed 0.5\% difference between the measured CKS
and {\it Kepler}\ rates\footnote{ \citet{petigura_CKS_2017} recently
found $\beta = 3.4^{0.9}_{-0.8}$.  If true, this implies that
metallicity could account for about half of the hot Jupiter rate
discrepancy.  }.  \citeauthor{guo_metallicity_2017}\!  concluded
that ``other factors, such as binary contamination and imperfect
stellar properties'' must also be at play.

Radial velocity surveys usually reject visual and spectroscopic
binaries~\citep{wright_frequency_2012}, so their hot Jupiter rates are
closer to the rate for single stars than the rates reported by transit
surveys.  However, we found in Section~\ref{sec:further_models} that
when assuming a Gaussian radius distribution, apparent hot Jupiter
rates are {\it greater} than the true rate around singles: the effect
goes the wrong way.  There could be other systematic factors behind
the difference~--~but they are unlikely to be related to binarity.

%in spectroscopic follow-up of transiting planet candidates, the
%prevalence of astrophysical false-positives may also lead to a
%tendency against confirming transiting planets in binary systems.  A
%separate observational bias is that the RV surveys typically observe
%chromospherically ``quiet'' stars, which may bias their detection
%probability high~\citep{bastien_radial_2014}.

\begin{comment}
  If we believe the assumed power law radius distribution, we can ask
  whether this ``correction factor'' might help resolve the
  discrepancy.  Explicitly, we ask: what is the probability of
  \citet{wright_frequency_2012}'s result, given a rate drawn from the
  stated bounds of~\citet{petigura_CKS_2017}?  In other words, we
  first take the true HJ rate per thousand stars as $\Lambda_{\rm HJ}
  = 5.7 \pm 1.3$, with Gaussian uncertainties.  We then draw from a
  Poisson distribution and compute the probability of detecting at
  least 10 hot Jupiters in a sample of 836 stars.  Without accounting
  for binarity or metallicity, only 4\% of RV surveys would detect at
  least 10 hot Jupiters.  If we multiply $\Lambda_{\rm HJ}$ by $1.2$
  to account for~\citet{guo_metallicity_2017}'s measured metallicity
  difference between the {\it Kepler}\ field and the local solar
  neighborhood, 9\% of RV surveys would detect at least 10 hot
  Jupiters.  If we multiply once more by $1.13$ to account for
  binarity's supposed bias, we find that 14\% of RV surveys would
  detect at least 10 hot Jupiters, still suggesting a weak
  discrepancy.  This suggestion should be taken with caution, because
  it (incorrectly) assumes a power law radius distribution.
\end{comment}

\paragraph{Does a detected planet orbit the primary or secondary?}

A separate reason to address stellar multiplicity in transit surveys
is that it can radically alter the interpretation of planet candidates
on a system-by-system level.  To identify and correct for unseen
stellar companions, high-resolution imaging campaigns have surveyed
almost all {\it Kepler}\ Objects of Interest~\citep{
  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been summarized
by~\citet{furlan_kepler_2017}, and they represent an important advance
in understanding the KOI sample's multiplicity statistics.

An immediate application is to reassess the radii of detected planets.
Doing so, \citet{hirsch_assessing_2017} recently found that for their
sample of KOIs in binaries, the planet radii are underestimated by
factors $r/r\a = 1.17$ if all planets orbit primaries, and $r/r\a =
1.65$ if detected planets are equally likely to orbit primaries and
singles.  This approach makes minimal assumptions about the likelihood
that a planet orbits the primary vs.~the secondary
(though~\citealt{hirsch_assessing_2017} do also consider weighting
radius corrections by planet occurrence).

Our approach provides a suggestion of how to assess the probability
that a detected planet in a binary system orbits either component.
The problem requires assuming both the underlying radius distribution,
and the relative number of planets per primary and secondary star.  We
found that for a broken power law radius distribution, with equal
occurrence rates about primaries and secondaries, detected planets in
binary systems are usually more likely to orbit the primary
(Figure~\ref{fig:frac_model_3}).  For apparent radii greater than
$2r_\oplus$, the odds of primary:secondary are 8:3.  The odds increase
for the planet to orbit the secondary increase at smaller apparent
radii, and reach 1:1 at $r\a=0.4r_\oplus$.  For {\it Kepler}, this
suggests that for almost all confirmed KOIs in multiple star systems,
the planet most likely orbits the primary.

\paragraph{Fraction of detected planets with binary companions}
A related effect is that some detected planets are more likely to be
in binary systems than others.  Notably, Figure~\ref{fig:frac_model_3}
predicts that the fraction of detected planets with binary companions
should increase by $6$~to~$12\%$ going from $2r_\oplus$ to
$1.4r_\oplus$.

In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
survey, they reported the fraction of planet-hosting stars with
Robo-AO detected companion stars, binned over apparent planet radii.
The fraction of KOIs with nearby stars and their $1\sigma$
uncertainties are:
\begin{itemize}
    \item Earths ($r\a < 1.6r_\oplus$): $16.3 \pm 1.0\%$, from 1480
    systems.
    \item Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$): $13.0 \pm
    0.8\%$, from 2058 systems.
    \item Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
    \item Jupiters ($r\a > 9r_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
\end{itemize} 
The uncertainties were calculated
following~\citet{burgasser_binarity_2003}.  The absolute values of the
companion fractions are lower than in the solar neighborhood at
least in part because of Robo-AO's sensitivity
(\citealt{ziegler_robo-ao_2017}'s
Figure~2;~\citealt{raghavan_survey_2010}).
%Another reason for the lower measured companion fraction could be
%that planetary systems are more rare in binary systems,
%as~\citealt{kraus_impact_2016} found for close binary companions).
The uptick in the companion rate for Jupiters is likely tied to a
large astrophysical false positive rate~\citep{santerne_sophie_2012}.
Going from Neptunes to Earths, the data suggest a weak increase in the
detected planet companion fraction, perhaps of a few percent.  It will
be interesting to see whether this effect is borne out by further
observations.

@@

\section{Conclusion}
\label{sec:conclusion}

This study presented a framework for estimating the impact of
unresolved binaries on transit survey occurrence rates. From
the order-of-magnitude argument presented in
Section~\ref{sec:simplest}, we showed that for Sun-like stars in the
local neighborhood, typical twin binary fractions yield apparent
occurrence rates that are well within a factor of two of the true
rates for single stars.

@@

Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
\begin{itemize}
%
\item If single, primary, and secondary stars all host the same number
  of planets per star, and the planet radius distribution is a power
    law with the exponent reported by~\citet{howard_planet_2012}, then
    binarity influences apparent planet occurrence rates at the few
    percent level. This applies for apparent radii from $2r_\oplus$ to
    $17r_\oplus$ (Section~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with the
  \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
    occurrence below $2r_\oplus$, the rate density for radii below
    $2r_\oplus$ is overestimated. The magnitude of the error, $\Delta
    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
    smaller than current systematic uncertainties on the occurrence
    rates of Earth-sized planets, this implies that binarity could
    eventually become an important component of the $\eta_\oplus$
    error budget.
%
\item Binarity blurs sharp features in the radius distribution
  (Figure~\ref{fig:model_4}), to a degree that could affect precise
    measurements of the depth, width, and slope of
    the~\citet{fulton_california-_2017} radius gap.
    %in the event that
    %planets are not carefully vetted with high-resolution imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates
  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
    radius distribution, similar to that reported
    by~\citet{petigura_CKS_2017}.
%
\item Detected planets with apparent radii greater than $0.5r_\oplus$
  that are revealed by high-resolution imaging surveys to exist in
    binaries are more likely to orbit the primary
    (Figure~\ref{fig:frac_model_3}).
%
\item Near the break in occurrence as a function of planet
  radius at $2r_\oplus$, the fraction of detected planets with
    binary companions should increase by roughly $5$~to~$10\%$
    (Figure~\ref{fig:frac_model_3}).
\end{itemize}

These results are only strictly applicable for idealized transit
surveys meeting the criteria mentioned above.  For real transit
surveys, although our approach is only suggestive, we hope that it
provides a useful estimate for the systematic errors that can be
incurred by ignoring binarity in calculations of planetary occurrence
rates.

@@

This appendix derives Equation~\ref{eq:general_Gamma_a} through a more
straight-forward, but also more tedious, procedure than that of
Section~\ref{sec:general_formula}.   First, note that analogous to
Equation~\ref{eq:occ_rate_simple}, the apparent rate density $\Gamma\a$ can be
written
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \, \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}$ is the number of detected planets, per unit
$(r\a, M\a)$, with apparent radius $r\a$ orbiting stars of
apparent mass $M\a$.   The planets with $(r\a, M\a)$ are associated
with systems of many different planetary and stellar properties, so
$n_{\rm det}(r\a, M\a)$ is given by the convolution of the true rate
density, $\Gamma(r, M)$, and $\mathcal{N}_\star(r\a, M\a; r, M)$, the
number of searchable stars per unit $(r\a, M\a)$ that give $(r\a,
M\a)$  when the true system actually has properties $(r, M)$.
Mathematically,
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_i n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_i \int \mathrm{d}r \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \, \Gamma_i(r,M) \, p_{\rm tra}(r,M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the type of true host star (0: single, 1:
primary, 2: secondary).  The problem reduces to the evaluation of
\begin{equation}
    \mathcal{N}_\star^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and
secondaries in binaries.

\paragraph{Single stars} For $i=0$, 
\begin{equation}
    \mathcal{N}_\star^0(r\a,M\a; r,M)
    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, so
\begin{equation}
    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
    M\a) \, p_{\rm tra}(r\a, M\a).
\end{equation}

>>>>

To compute the apparent occurrence rate density, we need to make
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different.  For a given value of $r\a$, the
  number of binary systems in the searchable sample with mass ratio
  $(q, q+\mathrm{d}q)$ is
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\, {n_{\rm b}\over n_{\rm s}}
    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
To obtain the total number of searchable binaries,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$. The
result of the integration replaces ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

@@

\section{Summary and Discussion}
\label{sec:discussion}

Ignoring binarity introduces systematic errors to star and planet
counts in transit surveys, which in turn lead to biases in the derived
planet occurrence rates.  Thus far, occurrence rate calculations using
transit survey data have mostly ignored stellar
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
We do not claim to have solved this problem. Our aim was to clarify
the various effects and assess the size of the errors in various
situations. We hope that our formalism will also be useful to those
investigators who do attempt more realistic calculations of occurrence
rates.

The calculations presented in Section~\ref{sec:model_2} suggest that
for planets around Sun-like stars with periods shorter than a few
months and apparent radii exceeding $2\,R_\oplus$, binarity can
basically be ignored.  The errors are only of order a few percent.
For apparent radii below $2\,R_\oplus$, nature may not be as
forgiving.  The size of the effect depends on the true radius
distribution and in particular whether it continues to vary as
$\sim$$r^{-3}$ down to 1\,$R_\oplus$ and below.  The calculations
presented in Section~\ref{sec:model_3} suggest that the apparent rates
could be overestimated by as much as 50\%.

\paragraph{Earth-like planets} For the specific problem of calculating the occurrence rate
$\eta_\oplus$ of Earth-like planets with periods of order one year,
even a 50\% systematic error would not be the dominant source of
uncertainty at the moment.  Estimates by
\citet{youdin_exoplanet_2011},~\citet{petigura_prevalence_2013},~\citet{dong_fast_2013},~\citet{foreman-mackey_exoplanet_2014},
and~\citet{burke_terrestrial_2015} have found values of $\eta_\oplus$
ranging from $0.03$ to unity, with the wide variance arising from
small-number statistics as well as a host of other systematic
errors~\citep[see][Figure~17]{burke_terrestrial_2015}.  Rapid progress
is expected soon, though, and binarity will merit closer attention in
the future.  It may also be worth investigating the possible effects
of any dependence of occurrence rate densities on the period of the
binary.  Binaries with separations $\lesssim 10\,{\rm AU}$ could
provoke dynamical instabilities, leading to fewer Earth-like planets
per
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
  kraus_impact_2016}.  This would affect transit survey measurements
of $\eta_\oplus$ beyond our rough estimate.

\paragraph{Hot Jupiters} Another frequently discussed problem
involving occurrence rates is the discrepancy between the occurrence
rates of hot Jupiters that have been measured in different surveys, as
summarized in Table~\ref{tab:hj_rates}.  In particular, the California
Planet Search (CPS), a Doppler survey, found a higher rate ($12\pm 2$
per thousand stars) than the {\it Kepler} transit survey
($5.7^{+1.4}_{-1.2}$).  It has been suggested that unresolved binaries
in the {\it Kepler} sample might be an important factor, but the
calculations presented in Section~\ref{sec:further_models} suggest
that this is not the case.  We found that the effects of unresolved
binaries are likely to result in an overestimation of the hot-Jupiter
occurrence rate, which would worsen the discrepancy, rather than
relieve it. Some other possibilities are errors in stellar
classification of the {\it Kepler} stars, as well as differences in
the metallicity of the stars in each survey.  The occurrence rate of
hot Jupiters is known to vary strongly with stellar metallicity, with
$\Lambda \propto 10^{3.4{\rm [M/H]}}$ according to a recent
study~\citep{petigura_CKS_2017}.  \citet{guo_metallicity_2017} found
the mean metallicity of the {\it Kepler} stars to be [M/H]~$=-0.045\pm
0.009$, which is only slightly lower than that of the stars in the
Doppler survey, $-0.005\pm 0.006$.  Nevertheless, given the strong
dependence of occurrence on metallicity, even a difference of
$0.04$~dex could account for a factor of $10^{3.4\cdot 0.04} = 1.37$
in the occurrence rate.  After correcting for metallicity, the
discrepancy between the {\it Kepler} and CPS occurrence rates is
reduced to the 1.7$\sigma$ level.

\paragraph{Radius corrections} Another application of our formalism is
to help in those cases in which it is not clear whether the primary or
secondary star is the source of a transit signal.  By this point
almost all of the {\it Kepler}\ Objects of Interest have been examined
with high resolution imaging~\citep{
  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been summarized
by~\citet{furlan_kepler_2017}. Based on this information,
\citet{hirsch_assessing_2017} re-assessed the radius measurements of
the {\it Kepler} planets in binaries. They found that planet radii are
generally underestimated by a factor $r/r\a = 1.17$ if all planets
orbit primaries, and $r/r\a = 1.65$ if detected planets are equally
likely to orbit primaries and singles.  Our formalism provides a way
to assess the relative probabilities that a detected planet orbits the
primary or secondary star.  The calculations presented in
\S\,\ref{subsec:whichstar} suggest that in almost all cases the planet
most likely orbits the primary star.

\begin{comment}
% JNW: These 2 sections do not seem very interesting.
  {\paragraph{Fraction of detected planets with binary companions}
A related effect is that some detected planets are more likely to be
in binary systems than others.  Notably, Figure~\ref{fig:frac_model_3}
predicts that the fraction of detected planets with binary companions
should increase by $6$~to~$12\%$ going from $2R_\oplus$ to
$1.4R_\oplus$.

In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI
survey, they reported the fraction of planet-hosting stars with
Robo-AO detected companion stars, binned over apparent planet radii.
The fraction of KOIs with nearby stars and their $1\sigma$
uncertainties are:
\begin{itemize}
    \item Earths ($r\a < 1.6R_\oplus$): $16.3 \pm 1.0\%$, from 1480
    systems.
    \item Neptunes ($1.6R_\oplus < r\a < 3.9 R_\oplus$): $13.0 \pm
    0.8\%$, from 2058 systems.
    \item Saturns ($3.9R_\oplus < r\a < 9 R_\oplus$): $13.6 \pm 2.0\%$, from 338 systems. 
    \item Jupiters ($r\a > 9R_\oplus$): $19.0 \pm 2.8\%$, from 247 systems. 
\end{itemize} 
The uncertainties were calculated
following~\citet{burgasser_binarity_2003}.  The absolute values of the
companion fractions are lower than in the solar neighborhood at
least in part because of Robo-AO's sensitivity
(\citealt{ziegler_robo-ao_2017}'s
Figure~2;~\citealt{raghavan_survey_2010}).
%Another reason for the lower measured companion fraction could be
%that planetary systems are more rare in binary systems,
%as~\citealt{kraus_impact_2016} found for close binary companions).
The uptick in the companion rate for Jupiters is likely tied to a
large astrophysical false positive rate~\citep{santerne_sophie_2012}.
Going from Neptunes to Earths, the data suggest a weak increase in the
detected planet companion fraction, perhaps of a few percent.  It will
be interesting to see whether this effect is borne out by further
observations.}

@@

\begin{comment}
\section{Conclusion}
% JNW: Material seems redundant.
  This study presented a framework for estimating the impact of
unresolved binaries on transit survey occurrence rates. From
the order-of-magnitude argument presented in
Section~\ref{sec:simplest}, we showed that for Sun-like stars in the
local neighborhood, typical twin binary fractions yield apparent
occurrence rates that are well within a factor of two of the true
rates for single stars.

@@

Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
\begin{itemize}
%
\item If single, primary, and secondary stars all host the same number
  of planets per star, and the planet radius distribution is a power
    law with the exponent reported by~\citet{howard_planet_2012}, then
    binarity influences apparent planet occurrence rates at the few
    percent level. This applies for apparent radii from $2R_\oplus$ to
    $17R_\oplus$ (Section~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with the
  \citet{howard_planet_2012} exponent above $2R_\oplus$ and a constant
    occurrence below $2R_\oplus$, the rate density for radii below
    $2R_\oplus$ is overestimated. The magnitude of the error, $\Delta
    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
    smaller than current systematic uncertainties on the occurrence
    rates of Earth-sized planets, this implies that binarity could
    eventually become an important component of the $\eta_\oplus$
    error budget.
%
\item Binarity blurs sharp features in the radius distribution
  (Figure~\ref{fig:model_4}), to a degree that could affect precise
    measurements of the depth, width, and slope of
    the~\citet{fulton_california-_2017} radius gap.
    %in the event that
    %planets are not carefully vetted with high-resolution imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates
  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
    radius distribution, similar to that reported
    by~\citet{petigura_CKS_2017}.
%
\item Detected planets with apparent radii greater than $0.5R_\oplus$
  that are revealed by high-resolution imaging surveys to exist in
    binaries are more likely to orbit the primary
    (Figure~\ref{fig:frac_model_3}).
%
\item Near the break in occurrence as a function of planet
  radius at $2R_\oplus$, the fraction of detected planets with
    binary companions should increase by roughly $5$~to~$10\%$
    (Figure~\ref{fig:frac_model_3}).
\end{itemize}

These results are only strictly applicable for idealized transit
surveys meeting the criteria mentioned above.  For real transit
surveys, although our approach is only suggestive, we hope that it
provides a useful estimate for the systematic errors that can be
incurred by ignoring binarity in calculations of planetary occurrence
rates.
\end{comment}

@@

Here we present an alternative derivation of
Equation~\ref{eq:general_Gamma_a}.  We also generalize a bit further,
by allowing the occurrence rate density to depend on stellar mass $M$
as well as planet radius $r$.  We begin by writing the apparent rate
density $\Gamma\a$ as (in analogy to
Equation~\ref{eq:occ_rate_simple})
\begin{equation}
    \Gamma\a(r\a,M\a) = \frac{n_{\rm det}(r\a,M\a)}{N_\star(r\a,M\a)}
    \, \frac{1}{p_{\rm tra}(M\a)},
\label{eq:apparent_rate_density}
\end{equation}
where $n_{\rm det}(r\a,M\a)$ is the number of detected planets per
star with radius $r\a$ orbiting stars of apparent mass $M\a$, per unit
$r\a$ and $M\a$.  This collection of planets with the same apparent
properties actually includes planets with a variety of true sizes and
host star masses.  We may write $n_{\rm det}(r\a, M\a)$ as the
convolution of the true occurrence rate density, $\Gamma(r, M)$; and
$\mathcal{N}_\star(r\a, M\a; r, M)$, the number of searchable stars
per unit $(r\a, M\a)$ for which a planet with true properties $(r, M)$
would appear to be a planet with apparent properties $(r\a, M\a)$:
\begin{align}
    n_{\rm det}(r\a, M\a) &=
    \sum_{i=0}^2 n_{\rm det}^i(r\a, M\a) \\
    &=
    \sum_{i=0}^2 \int \mathrm{d}r \int \mathrm{d}M \,
    \mathcal{N}_\star^i(r\a,M\a; r,M)
    \,\Gamma_i(r,M) \, p_{\rm tra}(M),
    \label{eq:n_det}
\end{align}
where $i$ specifies the true type of host star, with 0 for single
stars, 1 for primary stars, and 2 for secondary stars.  We now proceed
to calculate $\mathcal{N}_\star^i(r\a,M\a; r,M)$.

\paragraph{Single stars}
For single stars,
\begin{equation}
    \mathcal{N}_\star^0(r\a,M\a; r,M)
    =\hat{\delta}(r\a-r)\hat{\delta}(M\a-M) N_\star^0(r,M),
\end{equation}
where $\hat{\delta}$ is the Dirac delta function.  Therefore,
\begin{equation}
    n_{\rm det}^0(r\a, M\a)=N_\star^0(r\a,M\a)\, \Gamma_0(r\a, 
    M\a) \, p_{\rm tra}(r\a, M\a).
\end{equation}
